I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-10 Paper/Paper_noProof.tex
bug in milp

As far as we know, no formal result states the relationship between the LP approximation and DeepPoly.
We state here and prove later that the LP abstraction is strictly more accurate than the DeepPoly abstraction. It actually corresponds to consider in DeepPoly both linear functions lower bounding the ReLU function, $ReLU{y} \geq 0$ and $ReLU{y} \geq y$, while DeepPoly consider exactly one.

\begin{theorem}
 Given $y \in [\alpha,\beta]$ with $\alpha < 0 < \beta$, the following two systems of constraints are equivalent:
 \vspace{-0.1cm}
 \begin{align*}
	 \hat{y} \leq y \quad \wedge \quad \hat{y} \leq \beta \cdot a \quad & \wedge \quad \hat{y} \geq 0, \quad \wedge \quad \hat{y} \geq y-\alpha \cdot (1-a), a \in [0,1] \\
	 \text{and} \quad \hat{y} \geq 0 \quad & \wedge \quad \hat{y} \geq y \quad \wedge \quad \hat{y} \leq \beta \frac{y-\alpha}{\beta-\alpha}
\end{align*}

\end{theorem}

>>>>

As far as we know, no formal result states the relationship between the LP approximation and DeepPoly.
We state here and prove later that the LP abstraction is strictly more accurate than the DeepPoly abstraction. It actually corresponds to consider in DeepPoly both linear functions lower bounding the ReLU function, $ReLU{y} \geq 0$ and $ReLU{y} \geq y$, while DeepPoly considers exactly one.

\begin{proposition}
	\label{LP}
 Given $y \in [\alpha,\beta]$ with $\alpha < 0 < \beta$, the following two systems 1) and 2) of constraints are equivalent:
 \vspace{-0.1cm}
 \begin{align*}
	 1) \quad \hat{y} \leq y \quad \wedge \quad \hat{y} \leq \beta \cdot a \quad & \wedge \quad \hat{y} \geq 0, \quad \wedge \quad \hat{y} \geq y-\alpha \cdot (1-a), \, a \in [0,1] \\
	 \text{and} \quad  2) \quad \hat{y} \geq 0 \quad & \wedge \quad \hat{y} \geq y \quad \wedge \quad \hat{y} \leq \beta \frac{y-\alpha}{\beta-\alpha}
\end{align*} 
\end{proposition}
